### 2017-10-11 Gruba/00-abstr.tex
v4.2
v4.2
v4.3
v4.3

\begin{abstract}
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute.
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

>>>>

\begin{abstract}
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} microblogs every minute.
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model. % \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

### 2017-10-11 Gruba/01-intro.tex
v4.3
v4.3

Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
In the realm of social network behavior research, few work has been done towards making use of grouping, which however has been proved to be effective in other fields.
This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.

@@

\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.

>>>>

Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating users. 
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic research.
This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.

@@

\stab(1) We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model as in existed research.

### 2017-10-11 Gruba/02-overview.tex
v4.3
v4.3

We consider people's \retg{} behavior in social media.
For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A microblog $Mb = (O, T, M, flag)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $Mb$ belongs (either created or \retd{}), the timestamp $T$ showing when $Mb$ is generated, the microblog message $M$ and a bit $flag$ denoting $Mb$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

@@

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = Mb.O$ and $Mb \in B_u$
%
Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising three subsystems: Data Storage, the central Processing Runtime and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.75\linewidth]{figures/architecture}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\stitle{Key Modules.}
In the heart of \sys{} lies the Key Modules, which consists of three major components as follows.
%\begin{enumerate}

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extraction and serve as the input of User Clustering.

@@

	\stab(3)  Group Modeling: For each group obtained by User Clustering, Group Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization.
For the time being, Profile Demonstrator presents \tbc{}.

>>>>

We consider people's \retg{} behavior in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

%All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the timestamp $T$ showing when $M_b$ is generated, the microblog message $M$ and a bit $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

@@

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$. 
%
Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.75\linewidth]{figures/architecture.pdf}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\stitle{Key Modules.}
In the heart of \sys{} lies Key Modules, which consists of three major components.
%\begin{enumerate}

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extraction module and serve as the input of User Clustering module.

@@

	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator for visualization.
%For the time being, Profile Demonstrator presents \tbc{}.

### 2017-10-11 Gruba/03-fe.tex
v4.3
v4.3

With the underlying data in Data Storage subsystem, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

\subsection{Info Feature}

\textit{Info Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (\#R_s,\ \#E_s,\ R_{ee},\ \#B_s,\ R_{oc},\ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of microblogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Category of Info}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_s \le 50 \ \& \ \#R_s \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_s}{\#R_s} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_s}{\#E_s} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Unlike \textit{Info Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min. Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
\end{itemize}

@@

Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.

\begin{definition}
\label{def:lexi}
A lexicon $L = \{t\}$ consists of a set of topics while each topic $t = \{c\}$ is associated with a list of cell words $\{c\}$. Each cell word $c$ refers to one unique word in $L$.
\end{definition}

\begin{definition}
\label{def:bw}
%used \label{def:blog} previously
With a given user $u$, each microblog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
\end{definition}

@@

In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.

@@

\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
Go to \textbf{Step 7}.

@@

As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
\begin{equation}
\label{eq:fu}
	F(u) = (I,\ H,\ P_f)
\end{equation}
where $I$, $H$ and $P_f$ refer to \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
And it could be written as a vector:
\begin{equation}
\label{eq:fu-flat}
	F(u) = (\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
\end{equation}
where each dimension refers to a data item of \sys{}.

>>>>

With the underlying Sina Microblog Data, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

\subsection{Basic Feature}

\textit{Basic Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (\#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
%Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
\multirow{4}{*}{$R_{ee}$} & \multirow{2}{*}{a ratio defined as the number of followers} \\
                   &                     \\
                   & \multirow{2}{*}{over that of followees, i.e., $\frac{\#R_u}{\#E_u}$} \\
                   & 						\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ \& \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Unlike \textit{Basic Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value for the number of owned microblogs $\#B_u$
	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally created, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min. Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
\end{itemize}

@@

Different from the straightforward notions of \textit{Basic Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.

\begin{definition}
\label{def:lexi}
A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$. Each cell word depicts an aspect of the topic.
\end{definition}

\begin{definition}
\label{def:bw}
%used \label{def:blog} previously
With a given user $u$, each microblog $b \in B_u$ could be decomposed into a set of words $w$.
\end{definition}

@@

Next, we shall present the ``mining'' process for interest features. 
In short, \sys{} employs a well established lexicon to discover the explicit interests of users.
In case no proper explicit interests are found, TF-IDF and Twitter-LDA are leveraged to explore the implicit interests, during which word2vector participates to provide the similarity between two words.

In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.

@@

\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set. %, i.e., $b = \{w\}$ where $b \in B_s(u)$.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, 
where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$, 
and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
Go to \textbf{Step 7}.

@@

As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
\begin{equation}
\label{eq:fu}
	F(u) = (I,\ H,\ P_f)
\end{equation}
where $I$, $H$ and $P_f$ refer to \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
And it could be written as a vector:
\begin{equation}
\label{eq:fu-flat}
	F(u) = (\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
\end{equation}
where each dimension refers to a data item of \sys{}.

### 2017-10-11 Gruba/04-uc.tex
v4.3
v4.3

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_s$, $\#E_s$, $R_{ee}$, $\#B_s$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

>>>>

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee}$, $\#B_u$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

### 2017-10-11 Gruba/05-gm.tex
v4.3
v4.3

\begin{definition}
\label{def:gm-it}
An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of microblog $b$.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

@@

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.

>>>>

\begin{definition}
\label{def:gm-it}
An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_{b.O}$, i.e., $f$ is a follower of  the owner of microblog $b$.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

@@

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_u$, \#$E_u$, $R_{ee}$, \#$B_u$, \#$W_r$\}.
